?????????????????

### 2022-11-22 article_1/Methodology.tex
Split LaTeX files

%\documentclass[paper]{geophysics}
\documentclass[manuscript,revised]{geophysics}

\usepackage{setspace}
\usepackage[colorlinks]{hyperref}
\hypersetup{colorlinks=true,linkcolor={blue},citecolor={blue},urlcolor={red}}

\usepackage{amsmath}
\usepackage[utf8x]{inputenc}
\usepackage{graphicx}
\graphicspath{ {./images/} } % images path

\usepackage{multirow} % for tables
\usepackage[table,xcdraw]{xcolor}
\usepackage{floatrow} % for caption on the top of the table

\usepackage[nameinlink, capitalise, noabbrev]{cleveref} % enhance refs

\usepackage[document]{ragged2e} % to justify text

%\usepackage{ragged2e}
\DeclareCaptionJustification{justified}{\justifying} 			% to justify figure caption
%\captionsetup{compatibility=false,justification=justified} 		% to justify figure caption
%\DeclareCaptionFormat{custom}{\textbf{#1#2}\textit{\small #3}}
\DeclareCaptionFormat{custom}{\textbf{#1#2}{\small #3}}
\captionsetup{compatibility=false, justification=justified, format=custom}

% An example of defining macros
\newcommand{\rs}[1]{\mathstrut\mbox{\scriptsize\rm #1}}
\newcommand{\rr}[1]{\mbox{\rm #1}}

% found it here: https://stackoverflow.com/questions/70705684/latex-get-figure-caption-to-align-with-image
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{blindtext} % Package to generate dummy text throughout this template 
\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.05} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics
\usepackage[english]{babel} % Language hyphenation and typographical rules

\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text

\usepackage{enumitem} % Customized lists
\setlist[itemize]{noitemsep} % Make itemize lists more compact

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[L]{Manuscript} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text

\setlength\parindent{24pt}
%\usepackage{float}
\usepackage{floatrow}
\usepackage{pdfpages}
\newsavebox\mysavebox

\usepackage{booktabs} % to import tables directly from python
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{?????????????????}
\renewcommand{\thefootnote}{\fnsymbol{footnote}} 
\ms{GEO-Example} % manuscript number

\address{
\footnotemark[1]BP UTG, \\
200 Westlake Park Blvd, \\
Houston, TX, 77079 \\
\footnotemark[2]Bureau of Economic Geology, \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924}

\author{Gelson Ferreira de Souza-Junior\footnotemark[1], Ricardo Ivan Ferreira da Trindade\footnotemark[1],  Leonardo Uieda\footnotemark[2]}
\date{June 2022}
\footer{Example}
\lefthead{Dellinger \& Fomel}
\righthead{\emph{Geophysics} example}

\maketitle
\justify

\begin{abstract}
\begin{singlespace}
Paleomagnetism is the main tool used in paleogeographic reconstructions, in which directional information of the past magnetic field is retrieved from ferromagnetic grains (l.s). Magnetic minerals have a wide range of size and composition that influence their magnetic properties and, consequently, their ability to record the directions of paleomagnetic fields. The signals obtained with classical paleomagnetic methodologies are vector averages that include all magnetic grains present in the samples, including the stable and unstable carriers. To improve the quality of the magnetic signal, it would be necessary to individually identify the magnetizations of the carriers of remanent magnetization, in order to isolate only the good registers of the geomagnetic field. This would allow obtaining more reliable paleomagnetic information, as well as possibly being effective for the paleomagnetic study of older rocks (e.g., Archean rocks), meteorites and even bodies with complex geological evolution. Therefore, this project aims to apply magnetic microscopy to identify the remanent magnetization directions of stable magnetic grains and, subsequently, invert these data in an attempt to recover the individual paleomagnetic directions of the magnetic carriers present in the thin-sections. If successful, a new precision methodology for paleomagnetic data acquisition will be implemented.

\noindent{\textbf{Keywords}: Paleomagnetism, magnetic microscopy, Euler deconvolution, inversion of magnetic data.}
\end{singlespace}
\end{abstract}

\section{Introduction}
%\onehalfspacing
\doublespacing

\noindent{Paleomagnetism is the study of the record of the Earth's magnetic field preserved in rocks, being the main tool, and the only quantitative method, used during paleogeographic reconstruction~\citep{Butler1992}. It is based on three basic assumptions: (i) the geomagnetic field can be approximated to the field created by a geocentric axial dipole (GAD) aligned with the Earth's axis of rotation over a period that eliminates paleosecular variation ($>10^4$ years)~\citep{McElhinny2000}; (ii) ferromagnetic minerals (l.s.) acquire natural remanent magnetization (NRM) parallel to the Earth's geomagnetic field~\citep{Dunlop1997, Tauxe2018}; and (iii) this acquired magnetization is recorded for a long period of time, depending on the physicochemical characteristics of the magnetized mineral, following Neél's Theory~\citep{Neel1949, Neel1955} and being also influenced by the geological processes by which the rocks were submitted.}

\noindent{The thermoremanent magnetizations (TRMs) of magnetic particles in geological materials are the main records of the direction of the geomagnetic field of the past \citep{DeGroot2014}. Iron oxides, such as magnetite, which is the most common magnetic mineral present in rocks~\citep{OReilly1984} and acquire TRM as they cool below their Curie temperature and subsequently this direction of magnetization is “frozen” upon reaching blocking temperature~\citep{Dunlop1997}. When the grains are small enough, and the magnetization is unidirectional homogeneous (single domain - SD), the acquisition and preservation of magnetic signals is physically supported by Néel's theory~\citep{Neel1949, Neel1955}, conserving the remanent magnetization for long periods of time, on the order of billions of years, and for this reason, they are considered “good recorders” of the paleomagnetic field. In addition to SD, pseudo-single domain (PSD) particles, in the flower and stable vortex states, can also preserve magnetization for periods on the order of the solar system age~\citep{Nagy2017}. On the other hand, Néel's theory does not cover larger particles (multi domain - MD), which have unstable remanent magnetization (e.g., caused by viscous reordering of magnetic domains,~\cite{DeGroot2014}), so they are particles with limited ability to record the geomagnetic field. In addition to the magnetic domain state, particles can still vary in composition, size and shape which causes changes in their magnetic properties. All these factors are crucial in determining stable remanence directions used in the calculation of paleomagnetic poles.}

\noindent{Classic techniques for obtaining paleomagnetic data, e.g., thermal demagnetization and alternating fields, are based on the progressive acquisition of the magnetization contained in cylindrical samples, usually of 10 cm$^3$. The magnetic signal of a single specimen is the result of the sum of moments contained in the assembly of ferromagnetic grains, including stable and unstable registers~\citep{DeGroot2021}. Although there are recent well-structured studies of imaging magnetic minerals in thin-sections \citep[e.g.,][]{Almeida2014, Farchi2017,  Glenn2017, Lima2014, Lima2009, Nichols2016, Weiss2007, DeGroot2018, DeGroot2021}, obtaining NRM directions of individual grains in the rock fabric remains, to the best of our knowledge, a challenge deeply explored only by \cite{DeGroot2021}. With the possibility of isolating the individual contributions of a fairly large number ($10^6$ $>$ N $>$ $10^7$) of stable magnetic particles (SD/PSD) the magnetic directions recovered, using the average of their NRM vectors, would have an accurate paleomagnetic response \citep{Berndt2016}, however such number of observations is unfeasible for the currently insufficient measurements scales of the equipaments \citep{DeGroot2018}.}

\noindent{Several branches of Earth Sciences have demonstrated the importance of the “spatiality" of data on a microscopic scale, mainly in Geochemistry and Geochronology, where it is possible to perform punctual analyzes and compositional maps, which allowed significant advances in the understanding of igneous, metamorphic and sedimentary processes~\citep[e.g.,][]{ Barnes2019, Davidson2007, Verberne2020}. In Paleomagnetism there has been an interest in point magnetic analyses, or microscale magnetic maps, from magnetic microscopy techniques~\citep{DeGroot2014, DeGroot2018, Lima2014, Weiss2007}. However, despite recent advances in this area, still there is no well-established inversion protocol to determine the magnetic vector direction of each individual ferromagnetic grains, nor the intensity of magnetization, without using additional information of the positioning and shape of these sources, such as micromagnetic tomography \citep[e.g.,][]{DeGroot2018, DeGroot2021, Fabian2019}, which is a measurement spatially even more limited than the magnetic microscopy itself.}

\noindent{This paper aims to give a new perspective in the methodological routine that carry out paleomagnetic studies in microscale allowing to retrieve the individual remanent magnetization direction of these stable magnetic carriers (SD and PSD), semi automatically and without any additional information. In this way, a larger area of the thin section can be scanned with the objective of increasing the number of observations and, therefore, increasing the reliability of the directional data obtained. We also intend to generate a micromagnetic analysis protocol in an open source software, based on the techniques that will be described below.}

%%%%%%%%%%%%%

@@

\noindent{Let $\bar{B}$ be the observed data vector, whose i-th element ${\bar{B}}_i$, $i= 1, 2, ..., N$, is a total field anomaly, resulting from the NRM contribution of each ferromagnetic particle (\emph{l.s.}), measured at position ($x_i$, $y_i$, $z_i$) (black dots, \cref{fig:MODEL}). In this cartesian coordinate system, x points to geographic north, y points east, and z points down. In general, the magnetic field that is produced in the thin section is the result solely and exclusively of the NRM contribution of the particles without considering the induced component, since the measurements carried out in the magnetic microscope are usually made under magnetic shielding conditions. Thereby, approximating the shape of ferromagnetic minerals (\emph{l.s.}) to NRM magnetizing spheric/punctual sources. According to \cite{Blakely1996} the equation of a uniformly magnetized sphere is given by:}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\textwidth]{MODEL.pdf}
\caption{Schematic representation of spheres (L = 2) uniformly magnetized in the subsurface, whose magnetic effect, produced by these spheres, can be observed at points ($x_i$, $ y_i$, $z_i$), i = 1, 2, ..., N (black dots). In this cartesian coordinate system, x points to geographic north, y points east, and z points down. Modified from: \cite{OliveiraJr.2015}.}
\label{fig:MODEL}
\end{figure}

@@

@@

\noindent{In paleomagnetic studies the magnetization vectors are represented in terms of their declination (D) and inclination (I). These are given as a function of the magnetization vector ${\bar{m}}_j$ (\cref{eq:sphere8}) and represented in spherical coordinates (as shown in \cref{fig:VECTORS}).}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\textwidth]{VECTORS.pdf}
\caption{Schematic representation of vector $m_j$ (\cref{eq:sphere8}) with elements $mx_j$, $my_j$ and $mz_j$ in cartesian coordinates. This vector has declination $D_j$ (positive clockwise) and slope $I_j$ (positive downwards), j = 1, 2, ... L. Modified from: \cite{OliveiraJr.2015}.}
\label{fig:VECTORS}
\end{figure}

@@

\begin{equation} \label{eq:sphere19}
\centering
\small \bar{\bar{Cov}}\left(\widetilde{m_j}\right)=\ {\sigma_0}^2\cdot\left({\bar{\bar{A}}}^T\cdot ~ {\bar{\bar{R}}}^k\cdot ~ \bar{\bar{A}}\right)^{-1} \ \ \text{(\emph{robust})}
\end{equation}

\noindent{The main diagonal of the covariance matrix  (\cref{eq:sphere18} and \cref{eq:sphere19}) contains the variance of each member of the parameter vector, as expressed below:}

@@

\noindent{Thus, the propagation of uncertainties of the declination ($D_j$), inclination ($I_j$) and magnetic moment ($m_j$) results are given as a function of the parameters (detailed in Appendix A.2) obtained in \cref{eq:sphere20}:}

@@

%%%%%%%%%%%%%
\section{Results}

%%%
\subsection{Synthetic Data}

\noindent{We applied the proposed method in a numerical simulation of a geological thin-section of dimensions 1000 μm x 1000 μm in a regular grid (1000 x 1000) for estimating the magnetization directions of four spherical sources uniformly magnetized (but with different directions), according to \cref{tab:ModelTab}. Totaling an observation number N = $10^6$ obtained at a sensor-sample distance of 5 μm and a grid spacing of 1 μm. Subsequently, the data vector was contaminated with a pseudo-random noise of normal Gaussian distribution with a zero mean and 25 nT standard deviation, as shown in \cref{fig:SimpleSynthetic}a.}

\begin{figure}[htbp]
\centering
\includegraphics[width=1.0\textwidth]{SimpleSynthetic.png}
\caption{blablabla.}
\label{fig:SimpleSynthetic}
\end{figure}

\floatsetup[table]{capposition=top} % to put the caption on the top of the table

% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\input{input_par_table}

\subsubsection{Euler Solution}

\noindent{The first step is to calculate the magnetic horizontal gradient in order to isolate the window data of each source. In the horizontal gradient, the magnetic anomaly caused by a body tends to overlap its limits, thus obtaining a robust positioning \citep{Blakely1996}.  \cite{VanderWalt2014}.}

% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\input{solution_par_table}

\section{Discussion}

\section{Conclusion}
\noindent{We developed an efficient semi-automated method to determine the direction of magnetization of dipolar sources on a microscale, as well as the recovery of their magnetic moment. Being ideal for a reinterpretation for the application of methods of paleomagnetic studies using thin sections of rock samples. This would be an attempt to improve the quality of results obtained by isolating the responses of more reliable recorders of the Earth's geomagnetic field. }

\noindent{We also present a new, faster and cleaner way to solve the Euler equation in determining the positioning of magnetic anomaly sources using a pre-selection of magnetic anomaly source windows based on the Laplacian of the Gaussian applied to total gradient anomaly maps. In this way, reducing the numerous solutions to just one data window per source. After estimating the structural index (N=3) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler deconvolution is performed and the central position of each source is determined.}

\noindent{Since for the recovery of direction and magnetization we only need to assume that the sources have their central positions known (so we apply Euler deconvolution) and that their magnetizations are uniform. This last premise aligns with the theory of magnetically stable particles, which are the basis of classical paleomagnetism. Also, there is no need for any kind of prior knowledge other than the observed magnetic anomaly, and the structural index of the sources. Therefore, this method can be quickly replicated in a dataset of thin sections of rocks to obtain the distributions of magnetic directions of each source identified in the sample.}

\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions \ref{AppendixA.1} }

\begin{singlespace}
\doublespacing
\bibliographystyle{agu}  % style file is seg.bst
\bibliography{article1}
\end{singlespace}

\section{Appendix A}
\subsection{Appendix A.1} \label{AppendixA.1}

\noindent{As the least squares estimate (\cref{eq:sphere11}) is very sensitive to the presence of outliers in the observed data, the estimated parameters could be seriously misleading. To counteract this problem \cite{OliveiraJr.2015} suggest a robust scheme based on the minimization of the objective function obtained with the absolute error:}

\begin{equation} \label{eq:sphere12}
\centering
\small f\left(\widetilde{m}\right)=\left(\sum_{i=1}^{N}\left| { \left(\bar{\bar{A}} \cdot \bar{m} \right)}_{i} - {{\bar{\left(B_z\right)}}}_{i} \right|\right)
\end{equation}

\noindent{Unlike the solution presented for the objective function in \cref{eq:sphere11}, the parameter vector minimizing \cref{eq:sphere12} cannot be obtained as a simple linear system. A practical way is the iteratively reweighted least squares algorithm \citep{Aster2019, OliveiraJr.2015}. In this algorithm, at each iteration k, the following linear system is solved:}

\begin{equation} \label{eq:sphere13}
\centering
\small {\widetilde{m}}^{k+1}=\left({\bar{\bar{A}}}^T\cdot{\bar{\bar{R}}}^k\cdot\bar{\bar{A}}\right)^{-1}\cdot\left({\bar{\bar{A}}}^T\cdot{\bar{\bar{R}}}^k\cdot{\bar{B}}_z\right)\ \ 
\end{equation}

\noindent{The term ${\bar{\bar{R}}}^k$ is an N $\times$ N diagonal matrix whose i-th element $r_i^k$ (i = 1, 2, ..., N) is given by:}

\begin{equation} \label{eq:sphere14}
{r_i}^k=\frac{1}{\left|\left(\bar{\bar{A}}\cdot\bar{m}\right)_i-{{\bar{B_z}}}_i+e\right|}
\end{equation}

\begin{FlushRight}
\noindent{Where: $e$ is a small positive number used to prevent singularities}
\end{FlushRight}

\noindent{This iterative process starts (k = 0) with the solution vector obtained by the least squares estimator (\cref{eq:sphere11}). From this initial approximation ${\widetilde{m}}^0$, we calculate the matrix ${\bar{\bar{R}}}^0$ (\cref{eq:sphere14}). Which is used in the solution of the linear system given by \cref{eq:sphere13} to obtain the estimate ${\widetilde{m}}^1$. Later using this updated estimate to calculate the new matrix ${\bar{\bar{R}}}^1$ (\cref{eq:sphere14}), we solve the linear system (\cref{eq:sphere13}) to obtain a new estimate ${\widetilde{m}}^ 2$, and so on. As the iterations progress, this iterative procedure tends to converge and estimate $\widetilde{m}$, which is called robust estimate \citep{OliveiraJr.2015}. According to \cite{Aster2019} this convergence can be limited by a tolerance $\tau$, given by:}

\begin{equation} \label{eq:sphere15}
\centering
\frac{\lVert {\widetilde{m}}^{k+1} - {\widetilde{m}}^{k} \lVert}{1 + \lVert \widetilde{m}^{k+1} \lVert} ≤ \tau
\end{equation}

\begin{FlushRight}
\noindent{Where: $\tau$ is a positive number (\emph{e.g.}, ${10}^{-2}$) chosen by the algorithm user.}
\end{FlushRight}

\subsection{Appendix A.2} \label{AppendixA.2}

\begin{equation} \label{eq:sphere23}
\centering
\frac{\partial D_j}{\partial{mx}_j}=\frac{-{my}_j}{{{mx}_j}^2+{{my}_j}^2}
\end{equation}

\begin{equation} \label{eq:sphere24}
\centering
\frac{\partial D_j}{\partial{my}_j}=\frac{{mx}_j}{{{mx}_j}^2+{{my}_j}^2}
\end{equation}

\begin{equation} \label{eq:sphere25}
\centering
\frac{\partial I_j}{\partial{mx}_j}=\frac{-{mx}_j\cdot \ {mz}_j}{\sqrt{{{mx}_j}^2+{{my}_j}^2}\cdot \left({{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2\right)}
\end{equation}

\begin{equation} \label{eq:sphere26}
\centering
\frac{\partial I_j}{\partial{my}_j}=\frac{-{my}_j\cdot \ {mz}_j}{\sqrt{{{mx}_j}^2+{{my}_j}^2}\cdot \left({{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2\right)}
\end{equation}

\begin{equation} \label{eq:sphere27}
\centering
\frac{\partial I_j}{\partial{mz}_j}=\frac{\sqrt{{{mx}_j}^2+{{my}_j}^2}}{\left({{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2\right)}
\end{equation}

\begin{equation} \label{eq:sphere28}
\centering
\frac{\partial m_j}{\partial{mx}_j}=\frac{{mx}_j}{ \sqrt{{{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2} }
\end{equation}

\begin{equation} \label{eq:sphere29}
\centering
\frac{\partial m_j}{\partial{my}_j}=\frac{{my}_j}{ \sqrt{{{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2} }
\end{equation}

\begin{equation} \label{eq:sphere30}
\centering
\frac{\partial m_j}{\partial{mz}_j}=\frac{{mz}_j}{ \sqrt{{{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2} }
\end{equation}

\end{document}

>>>>

@@

\noindent{Let $\bar{B}$ be the observed data vector, whose i-th element ${\bar{B}}_i$, $i= 1, 2, ..., N$, is a total field anomaly, resulting from the NRM contribution of each ferromagnetic particle (\emph{l.s.}), measured at position ($x_i$, $y_i$, $z_i$) (black dots, \cref{fig:model_plus_vector}a). In this cartesian coordinate system, x points to geographic north, y points east, and z points down. In general, the magnetic field that is produced in the thin section is the result solely and exclusively of the NRM contribution of the particles without considering the induced component, since the measurements carried out in the magnetic microscope are usually made under magnetic shielding conditions. Thereby, approximating the shape of ferromagnetic minerals (\emph{l.s.}) to NRM magnetizing spheric/punctual sources. According to \cite{Blakely1996} the equation of a uniformly magnetized sphere is given by:}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{model_plus_vector.pdf}
\caption{a) Schematic representation of spheres (L = 2) uniformly magnetized in the subsurface, whose magnetic effect can be observed at points ($x_i$, $ y_i$, $z_i$), i = 1, 2, ..., N (black dots). In this cartesian coordinate system x, y and z corresponds to geographic north, east and z, respectively. b) Schematic cartesian representation of vector $m_j$ with elements $mx_j$, $my_j$ and $mz_j$, with declination $D_j$ (positive clockwise) and inclination $I_j$ (positive downwards), j = 1, 2, ... L. Modified from: \cite{OliveiraJr.2015}.}
\label{fig:model_plus_vector}
\end{figure}

@@

\noindent{The least squares estimator is also known to be affected by outliers in the data set \citep{Aster2019}. Since the environment of an SMM acquisition is very well controlled, the probability of occurrence of ouliers is considerably low. With that, in case there is an exception to the rule, we also implement a robust estimator to remove the influence of outliers \citep[Also adapted from:][]{OliveiraJr.2015}. This formulation is detailed in the~\nameref{AppendixA1}.}

@@

\noindent{In paleomagnetic studies the magnetization vectors are represented in terms of their declination (D) and inclination (I). These are given as a function of the magnetization vector ${\bar{m}}_j$ (\cref{eq:sphere8}) and represented in spherical coordinates (as shown in \cref{fig:model_plus_vector}b).}

@@

\noindent{The main diagonal of the covariance matrix  (\cref{eq:sphere18} contains the variance of each member of the parameter vector, as expressed below:}

@@

\noindent{Thus, the propagation of uncertainties of the declination ($D_j$), inclination ($I_j$) and magnetic moment ($m_j$) results are given as a function of the parameters (detailed in \nameref{AppendixA2}) obtained in \cref{eq:sphere20}:}

@@
